Social Attention for Autonomous Decision-Making in Dense Traffic

### 2020-07-28 paper/poster/poster.tex
Poster adjustements

\documentclass[a0paper,portrait,fontscale=0.3, margin=2cm]{baposter}

@@

\bibliography{../budgeted_rl.bib}

@@

%\background{ % Set the background to an image (background.pdf)
%\begin{tikzpicture}[remember picture,overlay]
%\draw (current page.north west)+(-2em,2em) node[anchor=north west]
%{\includegraphics[height=1.1\textheight]{background.png}};
%\end{tikzpicture}
%}
\begin{poster}{
grid=false,
borderColor=bordercol, % Border color of content boxes
headerColorOne=headercol1, % Background color for the header in the content boxes (left side)
headerColorTwo=headercol2, % Background color for the header in the content boxes (right side)
headerFontColor=headerfontcol, % Text color for the header text in the content boxes
boxColorOne=boxcolor, % Background color for the content in the content boxes
headershape=roundedright, % Specify the rounded corner in the content box headers
%headerfont=\Large\sf\bf, % Font modifiers for the text in the content box headers
headerfont=\Large\bf\textsc, %Sans Serif
textborder=rectangle,
background=none,
headerborder=open, % Change to closed for a line under the content box headers
boxshade=plain,
textfont={\setlength{\parindent}{0.0em}\sffamily},
headerheight={0.05\textheight},
eyecatcher=true
%columns=5
}
%
%----------------------------------------------------------------------------------------
%	Title and authors
%----------------------------------------------------------------------------------------
%
{
\includegraphics[width=10em]{./img/companies}
}
{
Social Attention for Autonomous Decision-Making in Dense Traffic
}
{
Edouard Leurent, Jean Mercat
\vspace{-4\baselineskip}
}
{
\includegraphics[width=12em]{./img/inria_sc}
}

\setlength{\colheight}{0.92\textheight}

@@

\begin{equation*}
Q^*(s, a) \eqdef \max_\pi \expectedvalue\left[\sum_{t=0}^\infty \gamma^t R(s_t, a_t)\condbar \substack{
s_0=s\\a_0=a
}
\right]
\end{equation*}

Bellman Optimality Equation:
\begin{equation*}
Q^*(s, a) = \expectedvalueover{s'\sim P(s'|s, a)} \max_{a'\in A} \left[R(s, a) + \gamma Q^*(s', a')\right]
\end{equation*}
}

@@

	\item \hlr{Sensitivity} to the ordering
	\begin{itemize}
		\item we want the policy to be \hlg{permutation-invariant}:
	\end{itemize}
\begin{align*}
\forall\tau \in \mathfrak{S}_N, \qquad &\pi(\cdot|(s_0, s_1,\dotsc,s_N)) = \\ &\pi(\cdot|(s_0, s_{\tau(1)},\dotsc,s_{\tau(N)}))
\end{align*}
\end{enumerate}

@@

\begin{itemize}[nolistsep]
	\item[\hlg{\checkmark}] Fixed-size
	\item[\hlg{\checkmark}] Does not depend on an ordering
	\item[\hlr{\xmark}] Suffers from an \hlr{accuracy / size tradeoff}
\end{itemize}

>>>>

\documentclass[paperwidth=36in,paperheight=48in,portrait,fontscale=0.3, margin=2cm]{baposter}

@@

\bibliography{../references.bib}

@@

%\background{ % Set the background to an image (background.pdf)
%\begin{tikzpicture}[remember picture,overlay]
%\draw (current page.north west)+(-2em,2em) node[anchor=north west]
%{\includegraphics[height=1.1\textheight]{background.png}};
%\end{tikzpicture}
%}
\begin{poster}{
grid=false,
borderColor=bordercol, % Border color of content boxes
headerColorOne=headercol1, % Background color for the header in the content boxes (left side)
headerColorTwo=headercol2, % Background color for the header in the content boxes (right side)
headerFontColor=headerfontcol, % Text color for the header text in the content boxes
boxColorOne=boxcolor, % Background color for the content in the content boxes
headershape=roundedright, % Specify the rounded corner in the content box headers
%headerfont=\Large\sf\bf, % Font modifiers for the text in the content box headers
headerfont=\Large\bf\textsc, %Sans Serif
textborder=rectangle,
background=none,
headerborder=open, % Change to closed for a line under the content box headers
boxshade=plain,
textfont={\setlength{\parindent}{0.0em}\sffamily},
headerheight={0.06\textheight},
eyecatcher=true
%columns=5
}
%
%----------------------------------------------------------------------------------------
%	Title and authors
%----------------------------------------------------------------------------------------
%
{
\includegraphics[height=1.7cm]{./img/companies}
}
{
Social Attention for Autonomous Decision-Making in Dense Traffic
}
{
Edouard Leurent$^*$, Jean Mercat$^*$
}
{
\includegraphics[height=2cm]{./img/inria_sc}
}

@@

Optimal Control Ojective
\begin{equation*}
Q^*(s, a) \eqdef \max_\pi \expectedvalue\left[\sum_{t=0}^\infty \gamma^t R(s_t, a_t)\condbar \substack{
s_0=s\\a_0=a
}
\right]
\end{equation*}

Bellman Optimality Equation and DQN Algorithm
\begin{equation*}
Q^*(s, a) = \expectedvalueover{s'\sim P(s'|s, a)} \max_{a'\in A} \left[R(s, a) + \gamma Q^*(s', a')\right]
\end{equation*}
}

@@

	\item \hlr{Sensitivity} to the ordering
	\begin{itemize}
		\item[\incarrow] we want the policy to be \hlg{permutation-invariant}:
	\end{itemize}
\begin{align*}
\forall\tau \in \mathfrak{S}_N, \qquad &\pi(\cdot|(s_0, s_1,\dotsc,s_N)) = \\ &\pi(\cdot|(s_0, s_{\tau(1)},\dotsc,s_{\tau(N)}))
\end{align*}
\end{enumerate}

@@

\begin{itemize}[]
	\item[\hlg{\checkmark}] Fixed-size
	\item[\hlg{\checkmark}] Does not depend on an ordering
	\item[\hlr{\xmark}] Suffers from an \hlr{accuracy / size tradeoff}
\end{itemize}
